---
title: "Setup"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Setup}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(ambientWeatherStation)
```

In order to use this package, you need:

* An Internet-enabled Ambient weather station
* The MAC address of the weather station
* An application key from Ambient
* An API key from Ambient (not the same as an app key)

You may have already located your station's MAC address in order to connect it to the Internet. If not, AmbientWeather.net has instructions for various models. For example, [here are the instructions for the WS-1000 serues](https://ambientweather.net/help/how-do-i-find-my-mac-address-ws-1000-series/).

To get your keys, log into your account at AmbientWeather.net and go to your account settings -- at the time this vignette was created, settings were at [https://dashboard.ambientweather.net/account](https://dashboard.ambientweather.net/account).

You should see instructions along with buttons and/or links to create an application key and API key.For more information about keys and the Ambient Weather API, see the [API documentation](https://ambientweather.docs.apiary.io/#).

### Using your MAC address and keys

The `ambient_get_wx()` function needs your MAC address, app key, and API key each time it's called. You can input them all manually as arguments every time. However, an easier way is to store them all in your R environment. The usethis package and RStudio make this easy. Run `edit_r_environ()` and then add the following lines to your .Renviron file:

```
AMBIENT_MAC_ADDRESS="your device's MAC address"
AMBIENT_APP_KEY="your application key"
AMBIENT_API_KEY="your API key"
```

Save the .Renviron file. You will need to restart your R session for those new values to be available. 

You should now be ready to run `ambient_get_wx()`!


